Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-09-14 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x

>>>>

############### M, SD, min, max of the perceived "Disruptive Person"
number.perceived.disrup.table <-
  df_no_outliers_ttff %>%
  group_by(Group, N) %>%
  summarise(
    N = n(),
    "M in sec" = round(mean(N), digits = 2),
    "SD in sec" = round(sd(N), digits = 2),
    "Min in sec" = round(min(N), digits = 2),
    "Max in sec" = round(max(N), digits = 2)
  )

knitr::kable(number.perceived.disrup.table,
             caption = "N, M, SD, min & max time to first fixation in seconds (AOI disruptive person)")
